---
title: "FML -1"
author: "Chandu"
date: "`r Sys.Date()`"
output: html_document

# 1: Download a dataset from the web. You may use any source, but specify the source in your code. Also ensure that the data has a mix of quantitative and qualitative (categorical) variables.
# 2. Import the dataset into R
```{r}
# Load data set
clothes_data <- read.csv("C:/Users/its me/OneDrive - Kent State University/Desktop/chandu/RHISTORY/clothes_price_prediction_data.csv")

```
# 3: Print out descriptive statistics for a selection of quantitative and categorical variables.
```{r}
# Descriptive statistics for quantitative variables
summary(clothes_data$Price)


# Descriptive statistics for categorical variables
table(clothes_data$Brand)

```
# 4: Transform at least one variable. It doesn't matter what the transformation is.

```{r}

# Log-transform the price variable
clothes_data$log_price <- log(clothes_data$Price)


```

# 5: Plot at least one quantitative variable, and one scatterplot
```{r}
# Histogram for the price variable
hist(clothes_data$Price, main = "Histogram of Price", xlab = "Price")


clothes_data <- na.omit(clothes_data)
clothes_data$Brand <- as.factor(clothes_data$Brand)


# Scatterplot for Price vs. Brand
plot(clothes_data$Price, clothes_data$Brand, 
     main = "Scatterplot: Price vs. Brand", 
     xlab = "Price", ylab = "Brand")
```

