---
title: "Assignment 4"
author: "Chandu"
date: "`r Sys.Date()`"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading the Required packages

```{r}
library(flexclust)
library(cluster)
library(tidyverse)
library(factoextra) 
library(FactoMineR)
library(ggcorrplot)
```

## 1.Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) used, the number of clusters formed, and so on.



### Loading the data

```{r}
pharma <- read.csv("C:\\Users\\its me\\OneDrive - Kent State University\\Desktop\\Rhistory\\Pharmaceuticals.csv")

head(pharma)
```

## At present, choose columns 3 through 11 and enter the information into variable Info 1.
```{r}

pharma1 <- pharma[3:11]
head(pharma1)
summary(pharma1)
```

### The various weights assigned to each variable along the rows will be used to scale the data in pharma1 and the pharma updated data frame. calculating the distance between the rows of data and displaying the distance matrix using the get dist(distance) and fviz dist(distance) functions of the factoextra package

```{r}
norm_data <- scale(pharma1)
row.names(norm_data) <- pharma[,1]
distance <- get_dist(norm_data)
corr <- cor(norm_data)
fviz_nbclust(norm_data,kmeans,method = "silhouette")
```

### Make a correlation matrix and print it to examine the relationship between the important variables.


```{r}
corr <- cor(norm_data)
ggcorrplot(corr , outline.color = "grey50", lab = TRUE, hc.order = TRUE ,type ="full")
```

*The Correlation Matrix shows that the ROA, ROE, Net Profit Margin, and Market Cap are all high*

### Principal component analysis will be used to figure out the relative importance of each of the key variables in the data collection.  


    Assuming the optimal cluster size is 5

```{r}
pca <- PCA(norm_data)
var <- get_pca_var(pca)
fviz_pca_var(pca, col.var="contrib",
             gradient.cols = c("orange","brown","green","red","black"),ggrepel = TRUE ) + labs( title = "PCA Variable Variance")
```

### We can assume from PCA Variable Variance that ROA, ROE, Net Profit Margin, Market Cap, and Asset Turnover contribute more than 61% to the two PCA components/dimensions, using the elbow technique to figure out the optimal customer base changeables.


```{r}

set.seed(10)

wss <- vector()
for(i in 1:10) wss[i] <- sum(kmeans(norm_data,i)$withinss)
fviz_nbclust(norm_data, kmeans, method = "wss")
wss
```

*The optimal cluster is at number 5 just as expected*

## Determining the optimal cluster size.

### Silhouette*

```{r}
fviz_nbclust(norm_data, kmeans, method = "silhouette")
```

  This indicates that the ideal number of clusters is five. forming five clusters with the k-means algorithm.

```{r}
set.seed(1)
k5 <- kmeans(norm_data, centers = 5, nstart = 31) # k = 5, number of restarts = 31
k5$centers 
k5$size  
fviz_cluster(k5, data = norm_data) 
```

#### Manhattan Distance when Kmeans Clustering is applied.

```{r}
set.seed(15)
k51 = kcca(norm_data, k=5, kccaFamily("kmedians"))
k51
```

####Utilizing the predict function
```{r}
clusters_index <- predict(k51)
dist(k51@centers)
image(k51)
points(norm_data, col=clusters_index, pch=19, cex=0.9)
```

## 2.Interpret the clusters with respect to the numerical variables used in forming the clusters Using Kmeans method to calculate Mean.

```{r}

pharma1%>% mutate(Cluster = k5$cluster) %>% group_by(Cluster) %>% summarise_all("mean")

clusplot(norm_data,k5$cluster, main="Clusters",color = TRUE, labels = 2,lines = 0)
```

*Companies are divided into several clusters, which include:*

** Cluster 1: MRX,ELN, AVE and WPI **

** Cluster 2: PHA+ and AGN **

** Cluster 3: AHM,WYE,BMY,AZN, LLY, ABT, NVS and SGP **

** Cluster 4: BAY, CHTT and IVX **

** Cluster 5: JNJ, MRK, PFE and GSK **

*The following can be obtained from the cluster variable means:*

** Cluster 1 has the fastest sales growth, the lowest PE ratio, and the best net profit margin. It can be purchased or held in reserve.**
 
** Cluster 2 PE ratio is extremely high.**

** Cluster 3 has a moderate risk.**

** Cluster 4 It has a great PE ratio, but because of its weak Net Profit margin, high leverage, and high risk, it is an exceptionally risky stock to purchase. Revenue growth is likewise extremely low.**

** Cluster 5 possesses high market capitalization, return on investment (ROI), return on assets(ROA), (ROA) return on asset turnover, and (ROA) return on net profit margin. A low price-to-earnings ratio suggests that the business is appropriately valued and can be purchased and held. An 18.5% increase in revenue is also beneficial.**

### 2B In relation to the numerical variables (10 to 12), are there any patterns in the clusters?

   By comparing clusters to the variables, we may observe patterns.

```{r}
Info_2 <- pharma[12:14] %>% mutate(Clusters=k5$cluster)
ggplot(Info_2, mapping = aes(factor(Clusters), fill =Median_Recommendation))+geom_bar(position='dodge')+labs(x ='Clusters')
ggplot(Info_2, mapping = aes(factor(Clusters),fill = Location))+geom_bar(position = 'dodge')+labs(x ='Clusters')
ggplot(Info_2, mapping = aes(factor(Clusters),fill = Exchange))+geom_bar(position = 'dodge')+labs(x ='Clusters')
```

    The variable grouped together, The median recommendations indicate a pattern.
    
    Other than the fact that most of the clusters/companies are based in the United States and are listed on the NYSE, there doesn't seem to be a clear trend among the locations, exchanges, or clusters.

    

## 3. Provide an appropriate name for each cluster using any or all of the variables in the data set.

Market Cap, Beta, PE Ratio, ROE, ROA and Asset Turnover are the factors that I have taken into consideration when naming the clusters. and with that information, I have defined the Clusters.


*Cluster 1: Profitable Giants*

Significant market capitalization, low beta, low PE ratio, strong ROE, ROA, and asset turnover are indicators of this. These organizations stand for strong, successful leaders in the business sector.

*Cluster 2: High Beta, High Risk Players*

Cluster 2 represents businesses with higher risk levels and is identified by heightened Beta and PE Ratio. Due to potential overvaluation and increasing market sensitivity, investors should proceed with caution.

*Cluster 3: Balanced Performers*

Cluster 3 represents the businesses in a moderate-risk category by balancing the Market Cap, Beta and PE Ratio. These well-balanced performers represents both the potential and stability.
  
*Cluster 4: High Risk, Low Efficiency* 

Entities in  the Cluster 4 experience very high risk despite having a great PE Ratio; low efficiency is illustrated by low ROE, ROA and asset turnover. This cluster is thought to be less effective and high-risk.

*Cluster 5: Efficient Powerhouses*

  Cluster 5 presents businesses with a gently valued PE Ratio along with strong efficiency measures, such as high ROE, ROA, and asset turnover. These effective powerhouses are essential for acquisition and as  well as retention.
